The \dealii Library, Version 9.7

### 2025-08-16 9.7/paper.tex
fix acknowledge

\begin{figure}[hb]
\label{fig:tbb-vs-taskflow}
\includegraphics{kokkos-vs-tbb/plots-figure1.pdf}\hfill
\includegraphics{kokkos-vs-tbb/plots-figure2.pdf}
\caption{Assembly times in a modified step-32 (left: temperature matrix assembly, right: temperature right-hand side assembly) comparing TBB and Taskflow with and without coloring.}
\end{figure}

@@

T.~Heister was also partially supported by NSF Awards OAC-2015848 and EAR-1925575.

T.~Heister was also partially supported by NSF OAC-2410848.

@@

>>>>

\begin{figure}[hb]
\includegraphics{kokkos-vs-tbb/plots-figure1.pdf}\hfill
\includegraphics{kokkos-vs-tbb/plots-figure2.pdf}
\caption{Assembly times in a modified step-32 (left: temperature matrix assembly, right: temperature right-hand side assembly) comparing TBB and Taskflow with and without coloring.}
\label{fig:tbb-vs-taskflow}
\end{figure}

@@

T.~Heister was also partially supported by NSF Awards OAC-2015848, EAR-1925575, and OAC-2410848.

@@

This research used in part resources on the Palmetto Cluster at Clemson University under National Science Foundation awards MRI 1228312, II NEW 1405767, MRI 1725573, and MRI 2018069. The views expressed in this article do not necessarily represent the views of NSF or the United States government.
